---
title: "Magenta Module Disease Activity Plots"
output: html_document
---

```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(rstatix)
library(ggpubr)
library(car)

setwd("~/VascMicroarray/Usable Data/")

phenodata <- read.csv("Phenodata.csv")
load(file = "VascNetworkConstruction.RData")
```

## Magenta Eigengene analysis

Creating a data frame with values for future analysis plus Magenta ME
One-way ANOVA with Tukey post-hoc test
```{r magenta}
magentaME <- MEs$MEmagenta
timepoint <- phenodata$timepoint_short
diagnosis <- phenodata$diagnosis_short
anca <- phenodata$ANCA_short
crp <- phenodata$crp
bvas <- phenodata$BVAS
gfr <- phenodata$gfr
pr3_titre <- phenodata$pr3_titre
mpo_titre <- phenodata$mpo_titre

magenta <- cbind(magentaME, timepoint, diagnosis, anca, crp, bvas, gfr, pr3_titre, mpo_titre)
magenta <- as.data.frame(magenta)
magenta <- transform(magenta, magentaME = as.numeric(magentaME),
                     timepoint = as.character(timepoint),
                     diagnosis = as.character(diagnosis),
                     anca = as.character(anca),
                     crp = as.numeric(crp),
                     bvas = as.numeric(bvas),
                     gfr = as.numeric(gfr),
                     pr3_titre = as.numeric(pr3_titre),
                     mpo_titre = as.numeric(mpo_titre))
magenta$timepoint <- factor(magenta$timepoint, 
                            levels = c("untimed", "zero", "three", "twelve"))
magenta$diagnosis <- factor(magenta$diagnosis, 
                            levels = c("Healthy", "GPA", "MPA"))
magenta$anca <- factor(magenta$anca, 
                       levels = c("Healthy", "neg", "PR3", "MPO", "double"))

#Stats between MagentaME and Time
magenta_aov <- aov(magentaME ~ timepoint, data = magenta)
# Summary of the analysis
summary(magenta_aov)
#Determine which groups are significant
magenta_tuk <- magenta %>% 
    tukey_hsd(magentaME ~ timepoint)
magenta_tuk <-magenta_tuk %>% 
    add_xy_position(x = "timepoint")
magenta_tuk

#Stats between Magenta ME and Diagnosis
mag_diag_aov <- aov(magentaME ~ diagnosis, data = magenta)
# Summary of the analysis
summary(mag_diag_aov)
#Determine which groups are significant
mag_diag_tuk <- magenta %>% 
    tukey_hsd(magentaME ~ diagnosis)
mag_diag_tuk <-mag_diag_tuk %>% 
    add_xy_position(x = "diagnosis")
mag_diag_tuk
```

Plot Magenta ME over timepoints in boxplot
```{r}
pdf(file = "Magenta Module/Magenta module over time.pdf", height = 3, width = 4)
ggplot(magenta, aes(x = timepoint, y = magentaME)) +
    geom_boxplot(outlier.shape = NA, fill = c("skyblue1", "brown1", "darkorange1", "yellow2")) +
    scale_x_discrete(labels = c("HC", "AAV Zero", "AAV Three", "AAV Twelve")) +
    geom_jitter(width = 0.1, size = 0.7)+ 
    theme_classic() +
    labs(x = "Timepoint", y = "Magenta Eigengene") +
    stat_pvalue_manual(magenta_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = T)
dev.off()
```

Plot Magenta ME with Diagnosis in boxplot
```{r}
pdf(file = "Magenta Module/Magenta module and diagnosis.pdf", width = 4, height = 3)
ggplot(magenta, aes(x = diagnosis, y = magentaME)) +
    geom_boxplot(outlier.shape = NA, fill = c("skyblue1", "darkgreen", "darkmagenta")) +
    scale_x_discrete(labels = c("Healthy", "GPA", "MPA")) +
    geom_jitter(width = 0.1, size = 0.7)+ 
    theme_classic() +
    labs(x = "Disease", y = "Magenta Eigengene") +
    stat_pvalue_manual(mag_diag_tuk, label = "p.adj.signif", tip.length = 0.01)
dev.off()
```


Stats and Plot Magenta ME with ANCA status
```{r}
anca_magenta <-subset(magenta, !is.na(anca))

#Stats between Magenta ME and ANCA
mag_anca_aov <- aov(magentaME ~ anca, data = anca_magenta)
# Summary of the analysis
summary(mag_anca_aov)
#Determine which groups are significant
mag_anca_tuk <- anca_magenta %>% 
    tukey_hsd(magentaME ~ anca)
mag_anca_tuk <-mag_anca_tuk %>% 
    add_xy_position(x = "anca")
mag_anca_tuk

pdf(file = "Magenta Module/Magenta module and ANCA status.pdf", width = 4, height = 3)
ggplot(anca_magenta, aes(x = anca, y = magentaME)) +
    geom_boxplot(outlier.shape = NA, fill = c("skyblue1", "grey60", "darkgreen", "darkmagenta", "tan4")) +
    scale_x_discrete(labels = c("Healthy", "ANCA-", "PR3+", "MPO+", "PR3+MPO+")) +
    geom_jitter(width = 0.1, size = 0.7)+ 
    theme_classic() +
    labs(x = "ANCA status", y = "Magenta Eigengene") +
    stat_pvalue_manual(mag_anca_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = TRUE)
dev.off()
```


## CRP analysis

Creating a data frame with only samples that have a CRP value
One-way ANOVA with bonferroni post-hoc test
Plot CRP over time in Box plot
```{r crp_magenta}
crp_magenta <- subset(magenta, !is.na(crp))

#Stats between CRP and Time
crp_aov <- aov(crp ~ timepoint, data = crp_magenta)
# Summary of the analysis
summary(crp_aov)
#Determine which groups are significant
crp_tuk <- crp_magenta %>% 
    tukey_hsd(crp ~ timepoint)
crp_tuk <- crp_tuk %>% 
    add_xy_position(x = "timepoint")
crp_tuk

pdf(file = "CRP levels over time.pdf", height = 3, width = 4)
ggplot(crp_magenta, aes(x = timepoint, y = crp)) +
    geom_boxplot(outlier.shape = NA, fill = c("brown1", "darkorange1", "yellow2")) +
    scale_x_discrete(labels = c("AAV Zero", "AAV Three", "AAV Twelve")) +
    geom_jitter(width = 0.1, size = 0.7)+ 
    theme_classic() +
    labs(x = "Timepoint", y = "CRP (mg/dL)") +
    stat_pvalue_manual(crp_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = TRUE)
dev.off()
```

Magenta and CRP scatter plot
```{r}
pdf(file = "Magenta Module/Magenta module and CRP correlation.pdf", 
    height = 3, width = 5)
ggplot(crp_magenta, aes(x = crp, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2, show.legend = FALSE) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = "CRP (mg/dL)", y = "Magenta Eigengene") +
    theme_classic() +
    stat_cor(method = "pearson", label.x = 150, label.y = -0.05)
dev.off()
```

## BVAS analysis

Creating a data frame with only samples that have a BVAS value
One-way ANOVA with bonferroni post-hoc test
Plot BVAS over time in Box plot
```{r bvas_magenta}
bvas_magenta <- subset(magenta, !is.na(bvas))
bvas_magenta$timepoint <- factor(bvas_magenta$timepoint, 
                            levels = c("zero", "three", "twelve"))

#Stats between BVAS and Time
bvas_aov <- aov(bvas ~ timepoint, data = bvas_magenta)
# Summary of the analysis
summary(bvas_aov)
#Determine which groups are significant
bvas_tuk <- bvas_magenta %>% 
    tukey_hsd(bvas ~ timepoint)
bvas_tuk <- bvas_tuk %>% 
    add_xy_position(x = "timepoint")
bvas_tuk

pdf(file = "BVAS levels over time.pdf", height = 3, width = 4)
ggplot(bvas_magenta, aes(x = timepoint, y = bvas)) +
    geom_boxplot(outlier.shape = NA, fill = c("brown1", "darkorange1", "yellow2")) +
    scale_x_discrete(labels = c("AAV Zero", "AAV Three", "AAV Twelve")) +
    geom_jitter(width = 0.1, size = 0.7)+ 
    theme_classic() +
    labs(x = "Timepoint", y = "BVAS Score") +
    stat_pvalue_manual(bvas_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = TRUE)
dev.off()
```

Magenta and BVAS scatter plot
```{r}
pdf(file = "Magenta Module/Magenta module and BVAS correlation.pdf", 
    height = 3, width = 5)
ggplot(bvas_magenta, aes(x = bvas, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2, show.legend = FALSE) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = "BVAS Score", y = "Magenta Eigengene") +
    theme_classic() +
    stat_cor(method = "pearson", label.x = 23, label.y = -0.05)
dev.off()
```

BVAS and CRP scatter plot
```{r}
bvas_crp <- subset(magenta, !is.na(bvas)) 
bvas_crp <- subset(bvas_crp, !is.na(crp))

pdf(file = "CRP and BVAS correlation.pdf", height = 3, width = 5)
ggplot(bvas_crp, aes(x = bvas, y = crp)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = "BVAS Score", y = "CRP (mg/dL)") +
    theme_classic() +
    theme(legend.position = "top") +
    stat_cor(method = "pearson", label.x = 25, label.y = 10)
dev.off()
```

## GFR analysis

Creating a data frame with only samples that have a GFR value
One-way ANOVA with bonferroni post-hoc test
Plot BVAS over time in Box plot
```{r gfr_magenta}
gfr_magenta <- subset(magenta, !is.na(gfr))
gfr_magenta$timepoint <- factor(gfr_magenta$timepoint, 
                            levels = c("zero", "three", "twelve"))

#Stats between GFR and Time
gfr_aov <- aov(gfr ~ timepoint, data = gfr_magenta)
# Summary of the analysis
summary(gfr_aov)

pdf(file = "GFR levels over time.pdf", height = 3, width = 4)
ggplot(gfr_magenta, aes(x = timepoint, y = gfr)) +
    geom_boxplot(outlier.shape = NA, fill = c("brown1", "darkorange1", "yellow2")) +
    scale_x_discrete(labels = c("AAV Zero", "AAV Three", "AAV Twelve")) +
    geom_jitter(width = 0.1, size = 0.7)+ 
    theme_classic() +
    labs(x = "Timepoint", y = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")))
    #stat_pvalue_manual(gfr_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = TRUE)
dev.off()
```

Magenta and GFR scatter plot
```{r}
pdf(file = "Magenta Module/Magenta module and GFR correlation.pdf", 
    height = 3, width = 5)
ggplot(gfr_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2, show.legend = FALSE) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene") +
    theme_classic() +
    stat_cor(method = "pearson", label.x = 37, label.y = 0.25)
dev.off()
```


## PR3 vs MPO Analysis

Magenta Eigengene over time splitting by ANCA status
```{r split_magenta}
split_magenta <- magenta[diagnosis != "Healthy",]
split_magenta <- subset(split_magenta, anca != "double")
split_magenta <- subset(split_magenta, anca != "neg")
split_magenta$timepoint <- factor(split_magenta$timepoint,levels = c("zero", "three", "twelve"))
split_magenta$anca <- factor(split_magenta$anca, levels = c("PR3", "MPO"))

#Stats between Magenta and ANCA intersecting with Time
split_aov <- aov(magentaME ~ anca * timepoint, data = split_magenta)
# Summary of the analysis
summary(split_aov)
#Determine which groups are significant


pdf(file = "Magenta Module/Magenta module over time - PR3-MPO.pdf", height = 3, width = 4)
ggboxplot(split_magenta, x = "timepoint", y = "magentaME", fill = "anca", add = "jitter", shape = "anca", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta")) +
    labs(x = "Timepoint (months)", y = "Magenta Eigengene") +
    theme(legend.position = "none")
dev.off()
```

PR3 vs MPO for CRP levels
```{r split_crp}
split_crp <- subset(split_magenta, !is.na(crp))
#Stats between Magenta and ANCA intersecting with Time
split_crp_aov <- aov(crp ~ anca * timepoint, data = split_crp)
# Summary of the analysis
summary(split_crp_aov)
#No difference between ANCA status so no post-hoc

pdf(file = "CRP over time - PR3-MPO.pdf", height = 3, width = 4)
ggboxplot(split_crp, x = "timepoint", y = "crp", fill = "anca", add = "jitter", shape = "anca", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta"),
                      name = "ANCA") +
    labs(x = "Timepoint (months)", y = "CRP mg/dL") +
    theme(legend.position = "none")
dev.off()

```

PR3 vs MPO for BVAS levels
```{r split_bvas}
split_bvas <- subset(split_magenta, !is.na(bvas))
#Stats between Magenta and ANCA intersecting with Time
split_bvas_aov <- aov(bvas ~ anca * timepoint, data = split_bvas)
# Summary of the analysis
summary(split_bvas_aov)
#No difference between ANCA status so no post-hoc

pdf(file = "BVAS over time - PR3-MPO.pdf", height = 3, width = 4)
ggboxplot(split_bvas, x = "timepoint", y = "bvas", fill = "anca", add = "jitter", shape = "anca", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta"),
                      name = "ANCA") +
    labs(x = "Timepoint (months)", y = "BVAS Score") +
    theme(legend.position = "none")
dev.off()
```

PR3 vs MPO for GFR levels
```{r split_gfr}
split_gfr <- subset(split_magenta, !is.na(gfr))
#Stats between Magenta and ANCA intersecting with Time
split_gfr_aov <- aov(gfr ~ anca * timepoint, data = split_gfr)
# Summary of the analysis
summary(split_gfr_aov)
#Determine which groups are significant
split_gfr_tuk <- split_gfr %>% 
    group_by(timepoint) %>% 
    tukey_hsd(gfr ~ anca) %>% 
    ungroup()
split_gfr_tuk <- split_gfr_tuk %>% 
    add_xy_position(x = "timepoint")

pdf(file = "GFR over time - PR3-MPO.pdf", height = 3, width = 4)
ggboxplot(split_gfr, x = "timepoint", y = "gfr", fill = "anca", add = "jitter", shape = "anca", add.params = list(size = 1)) +
    scale_y_continuous(limits=c(0,70)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta")) +
    labs(x = "Timepoint (months)", y = expression(paste("GFR (mL/min/1.73m" ^ "2", ")"))) +
    theme(legend.position = "none") +
    stat_pvalue_manual(split_gfr_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = T, y.position = 65)
dev.off()
```

## GPA vs MPA analysis

Magenta eigengene over time
```{r diag_split_magenta}
diag_split_magenta <- magenta[diagnosis != "Healthy",]
diag_split_magenta$timepoint <- factor(diag_split_magenta$timepoint,
                                       levels = c("zero", "three", "twelve"))
diag_split_magenta$diagnosis <- factor(diag_split_magenta$diagnosis, 
                                       levels = c("GPA", "MPA"))

#Stats between Magenta and ANCA intersecting with Time
diag_split_aov <- aov(magentaME ~ diagnosis * timepoint, data = diag_split_magenta)
# Summary of the analysis
summary(diag_split_aov)
#Determine which groups are significant
diag_split_tuk <- split_gfr %>% 
    group_by(timepoint) %>% 
    tukey_hsd(magentaME ~ diagnosis) %>% 
    ungroup()
diag_split_tuk <- diag_split_tuk %>% 
    add_xy_position(x = "timepoint")
diag_split_tuk

pdf(file = "Magenta Module/Magenta module over time - GPA-MPA.pdf", height = 3, width = 4)
ggboxplot(diag_split_magenta, x = "timepoint", y = "magentaME", fill = "diagnosis", add = "jitter", shape = "diagnosis", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta")) +
    labs(x = "Timepoint (months)", y = "Magenta Eigengene") +
    theme(legend.position = "none") +
    stat_pvalue_manual(diag_split_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = T, y.position = 0.3)
dev.off()

#Magenta eigengene over time between GPA and MPA patients with GFR as a covariate
diag_split_aov_gfr <- aov(magentaME ~ diagnosis * timepoint + gfr, data = diag_split_magenta)
# Summary of the analysis
car::Anova(diag_split_aov_gfr, type = 2)
#GFR does not influence magentaME difference in diagnosis
```


GPA vs MPA for CRP levels
```{r diag_split_crp}
diag_split_crp <- subset(diag_split_magenta, !is.na(crp))
#Stats between Magenta and ANCA intersecting with Time
diag_split_crp_aov <- aov(crp ~ diagnosis * timepoint, data = diag_split_crp)
# Summary of the analysis
summary(diag_split_crp_aov)
#Determine which groups are significant
diag_split_crp_tuk <- diag_split_crp %>% 
    group_by(timepoint) %>% 
    tukey_hsd(crp ~ diagnosis) %>% 
    ungroup()
diag_split_crp_tuk <- diag_split_crp_tuk %>% 
    add_xy_position(x = "timepoint")
diag_split_crp_tuk

pdf(file = "CRP over time - GPA-MPA.pdf", height = 3, width = 4)
ggboxplot(diag_split_crp, x = "timepoint", y = "crp", fill = "diagnosis", add = "jitter", shape = "diagnosis", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta"),
                      name = "ANCA") +
    labs(x = "Timepoint (months)", y = "CRP mg/dL") +
    theme(legend.position = "none") +
    stat_pvalue_manual(diag_split_crp_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = T)
dev.off()

#CRP over time between GPA and MPA patients with GFR as a covariate
diag_split_crp_aov_gfr <- aov(crp ~ diagnosis * timepoint + gfr, data = diag_split_crp)
# Summary of the analysis
car::Anova(diag_split_crp_aov_gfr, type = 2)
#GFR effects difference in crp seen in different diagnosis
```

GPA vs MPA for BVAS levels
```{r diag_split_bvas}
diag_split_bvas <- subset(diag_split_magenta, !is.na(bvas))
#Stats between Magenta and ANCA intersecting with Time
diag_split_bvas_aov <- aov(bvas ~ diagnosis * timepoint, data = diag_split_bvas)
# Summary of the analysis
summary(diag_split_bvas_aov)
#No difference in diagnosis so post-hox not completed

pdf(file = "BVAS over time - GPA-MPA.pdf", height = 3, width = 4)
ggboxplot(diag_split_bvas, x = "timepoint", y = "bvas", fill = "diagnosis", add = "jitter", shape = "diagnosis", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta"),
                      name = "ANCA") +
    theme(legend.position = "none") +
    labs(x = "Timepoint (months)", y = "BVAS Score")
dev.off()
```

GPA vs MPA for GFR levels
```{r diag_split_gfr}
diag_split_gfr <- subset(diag_split_magenta, !is.na(gfr))
#Stats between Magenta and ANCA intersecting with Time
diag_split_gfr_aov <- aov(gfr ~ diagnosis * timepoint, data = diag_split_gfr)
# Summary of the analysis
summary(diag_split_gfr_aov)
#Determine which groups are significant
diag_split_gfr_tuk <- diag_split_gfr %>% 
    group_by(timepoint) %>% 
    tukey_hsd(gfr ~ diagnosis) %>% 
    ungroup()
diag_split_gfr_tuk <- diag_split_gfr_tuk %>% 
    add_xy_position(x = "timepoint")
diag_split_gfr_tuk

pdf(file = "GFR over time - GPA-MPA.pdf", height = 3, width = 4)
ggboxplot(diag_split_gfr, x = "timepoint", y = "gfr", fill = "diagnosis", add = "jitter", shape = "diagnosis", add.params = list(size = 1)) +
    theme_classic() +
    scale_x_discrete(labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("darkgreen", "darkmagenta")) +
    labs(x = "Timepoint (months)", y = expression(paste("GFR (mL/min/1.73m" ^ "2", ")"))) +
    theme(legend.position = "none") +
    stat_pvalue_manual(diag_split_gfr_tuk, label = "p.adj.signif", tip.length = 0.01, hide.ns = T, y.position = 65)
dev.off()
```

Magenta and GFR scatter plot for PR3 patients
```{r pr3_magenta}
pr3_magenta <- magenta[anca == "PR3",]
pr3_magenta <- subset(pr3_magenta, !is.na(gfr))

pdf(file = "Magenta Module/Magenta module and GFR correlation - PR3.pdf", 
    height = 3, width = 5)
ggplot(pr3_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene", title = "PR3 Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 37, label.y = 0.2)
dev.off()
```

Magenta and GFR scatter plot for MPO patients
```{r mpo_magenta}
mpo_magenta <- magenta[anca == "MPO",]
mpo_magenta <- subset(mpo_magenta, !is.na(gfr))

pdf(file = "Magenta Module/Magenta module and GFR correlation - MPO.pdf", 
    height = 3, width = 5)
ggplot(mpo_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene", title = "MPO Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 33, label.y = 0.15)
dev.off()
```

Magenta and GFR scatter plot for GPA patients
```{r gpa_magenta}
gpa_magenta <- magenta[diagnosis == "GPA",]
gpa_magenta <- subset(gpa_magenta, !is.na(gfr))

pdf(file = "Magenta Module/Magenta module and GFR correlation - GPA.pdf", 
    height = 3, width = 5)
ggplot(gpa_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene", title = "GPA Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 37, label.y = 0.2)
dev.off()
```

Magenta and GFR scatter plot for MPA patients
```{r mpa_magenta}
mpa_magenta <- magenta[diagnosis == "MPA",]
mpa_magenta <- subset(mpa_magenta, !is.na(gfr))

pdf(file = "Magenta Module/Magenta module and GFR correlation - MPA.pdf", 
    height = 3, width = 5)
ggplot(mpa_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene", title = "MPA Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 37, label.y = 0.25)
dev.off()
```



Magenta and pr3_titre scatter plot for PR3 patients
```{r pr3_magenta}
pr3_titre_magenta <- magenta[anca == "PR3",]
pr3_titre_magenta <- subset(pr3_titre_magenta, !is.na(pr3_titre))

pdf(file = "Magenta Module/Magenta module and pr3_titre correlation - PR3.pdf", 
    height = 3, width = 5)
ggplot(pr3_titre_magenta, aes(x = pr3_titre, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = "PR3 Titre (iu/mL)", y = "Magenta Eigengene", title = "PR3 Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 375, label.y = 0.2)
dev.off()
```

Magenta and mpo_titre scatter plot for MPO patients
```{r mpo_magenta}
mpo_titre_magenta <- magenta[anca == "MPO",]
mpo_titre_magenta <- subset(mpo_titre_magenta, !is.na(mpo_titre))

pdf(file = "Magenta Module/Magenta module and mpo_titre correlation - MPO.pdf", 
    height = 3, width = 5)
ggplot(mpo_titre_magenta, aes(x = mpo_titre, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 2) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = "MPO Titre (iu/mL)", y = "Magenta Eigengene", title = "MPO Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 375, label.y = 0.12)
dev.off()
```

GFR scatter plot for GPA patients with gfr < 60
```{r} 
gpa_magenta <- magenta[diagnosis == "GPA",]
gpa_magenta <- subset(gpa_magenta, !is.na(gfr))
gpa_renal_magenta <- subset(gpa_magenta, gfr < 60)

pdf(file = "Magenta Module/Magenta module and GFR correlation - GPA renal patients.pdf", 
    height = 3, width = 5)
ggplot(gpa_renal_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 3) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene", title = "GPA Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 37, label.y = 0.2)
dev.off()
```

GFR scatter plot for PR3 patients with gfr < 60
```{r}
pr3_magenta <- magenta[anca == "PR3",]
pr3_magenta <- subset(pr3_magenta, !is.na(gfr))
pr3_renal_magenta <- subset(pr3_magenta, gfr < 60)

pdf(file = "Magenta Module/Magenta module and GFR correlation - PR3 renal patients.pdf", 
    height = 3, width = 5)
ggplot(pr3_renal_magenta, aes(x = gfr, y = magentaME)) +
    geom_point(aes(color = timepoint, shape = timepoint, fill = timepoint),
               color = "black", size = 3) +
    scale_shape_manual(values = c(21, 22, 23), 
                       name = "Timepoint (months)", 
                       labels = c("Zero", "Three", "Twelve")) +
    scale_fill_manual(values = c("brown1", "darkorange1", "yellow2"),
                      name = "Timepoint (months)", 
                      labels = c("Zero", "Three", "Twelve")) +
    geom_smooth(method = lm, se = FALSE, colour = "skyblue1") +
    labs(x = expression(paste("GFR (mL/min/1.73m" ^ "2", ")")), y = "Magenta Eigengene", title = "PR3 Patients") +
    theme_classic() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none") +
    stat_cor(method = "pearson", label.x = 37, label.y = 0.2)
dev.off()
```


```{r}

```



